### 2015-06-25 Manuscript/BiologyLetters/Missing_mammals-draft.tex
Abstract edits

%---------------------------------------------
%
%       ABSTRACT
%
%---------------------------------------------
\newpage
\begin{abstract}
Combining living and fossil in the same analysis data is crucial for studying changes in global biodiversity through time.
One method allowing to combine this data is the Total Evidence method that uses both molecular data for living species and morphological data for both living and fossil species.
With this method, a good overlap of morphological data between living and fossil taxa is crucial for accurately inferring the phylogenies’ topology.

Since the advent of DNA, molecular data has become easily and widely available.
However, despite two centuries of morphological studies, scientists using and generating such data mainly focus on palaeontological data.
Therefore, there is a gap in our knowledge of neontological morphological data even in well studied groups such as mammals.

In this study, we quantify the morphological data available for living mammal taxa.
We then analyse the structure of the available data by testing if it is clustered or evenly spread across the phylogeny.
We found that 78\% of mammalian orders have less than 25\% data available at the species level.
However, we found that the available is often randomly distributed among these orders apart from six of them where the data is clustered
\end{abstract}

%\noindent Key words: Total Evidence method, phylogenetic clustering, morphological matrix, fossil, topology\\ Excluded from word count.

>>>>

%---------------------------------------------
%
%       ABSTRACT
%
%---------------------------------------------
\newpage
\begin{abstract}
\section{abstract} % NC: Just put this here as it then separates this for the word count
Analyses of living and fossil taxa are crucial for understanding changes in biodiversity through time.
The Total Evidence method allows living and fossil taxa to be combined in phylogenies, by using molecular data for living taxa and morphological data for both living and fossil taxa.
With this method, substantial overlap of morphological data among living and fossil taxa is crucial for accurately inferring topology.
However, although molecular data for living species is widely available, scientists using and generating morphological data mainly focus on fossils.
Therefore, there is a gap in our knowledge of neontological morphological data even in well-studied groups such as mammals.

We investigated the amount of morphological (cladistic) data available for living mammals and how this data was phylogenetically distributed across orders.
22 of 28 mammalian orders have \textless 25\% species with available morphological data; this has implications for the accurate placement of fossil taxa, although the issue is less pronounced at higher taxonomic levels. 
In most orders, species with available data are randomly distributed across the phylogeny, which may reduce the impact of the problem.
We suggest that increased morphological data collection efforts for living taxa are needed to produce accurate Total Evidence phylogenies. 
\end{abstract}

%\noindent Key words: Total Evidence method, phylogenetic clustering, morphological matrix, extinct, topology\\ Excluded from word count.
% NC: Might need some new ones as these are in the abstract now...
